A Fast and Tight Heuristic for A* in Road Networks

### 2021-01-20 paper/ch_potentials.tex
fix citations

There is a lot of work that extends hierarchical speed-up techniques to more complex settings.
\todo{cite overview}
% For example, in~\cite{fns-opca-14,gks-rpfof-10} multi-criteria optimization is studied.
MLD/CRP~\cite{dgpw-crprn-13} was developed to allow exchanging weights in reasonable time.
This enable user preferences and live traffic.
MLD/CRP also supports turn costs.
Integrating traffic predictions into CRP was studied in~\cite{bdpw-dtdrp-16}.
In~\cite{dsw-cch-15}, CH is extended to Customizable CH (CCH), which also supports exchanging weights and thus supporting user preferences and live traffic.
CH is extended to support turn costs in~\cite{}, CCH in~\cite{bwzz-cchtc-20}.
Traffic predictions are combined with CH in~\cite{swz-sfert-19,bgsv-mtdtt-13}.
\todo{cite correct CATCHUp Version}
\todo{improve! and discuss hierarchical extensions and what they achieve and their difficulties in more details}
Specialized variants for electric vehicle routing are developed in~\cite{DBLP:journals/algorithmica/BaumDPSWZ20,DBLP:conf/aaai/EisnerFS11}.
While these works show that it is possible to extend hierarchical approaches, they also show that it is non-trivial.
Further, in every setting the flexibility available at query time is fairly limited.
Combining all these hierarchical extensions is an unsolved problem.
%
CH-Potentials is not the first work to combine hierarchical approaches and A*~\cite{bdsssw-chgds-10,gkw-blwr-07,bdgwz-sfpcs-19}.
However, a lot of past works use A* to accelerate hierarchical approaches even further and loose A*'s flexibility.
\todo{cite traffic aware routing}
%

@@

The classical shortest path problem assumes that edge weights are scalars.
However in practice, travel times vary along an edge.
The primary reason is traffic.
Recurring traffic can be predicted by observing the traffic in the past.
It is common \cite{bgsv-mtdtt-13,bdpw-dtdrp-16,swz-sfert-19} to represent these predictions as \emph{travel time functions}.
An edge weight is no longer a scalar value but a function that maps the entry time onto the traversal time.
% Performing this prediction is outside of the scope of this paper.
It is common to refer to routing with predicted traffic as \emph{time-dependent routing}.
% Again, we first formalize the extended problem setting and then describe our solution with CH-Potentials.

@@

With this setup, we extended CH-Potentials to support time-dependent routing.
As we were able to keep all travel time functions out of the CH, we avoid a lot of algorithmic complications compared to~\cite{bgsv-mtdtt-13,bdpw-dtdrp-16,swz-sfert-19}, which create shortcuts of travel time functions to combine hierarchical speedup techniques with time-dependent routing.

@@

Truck routing differs from car routing due to night driving bans and other restrictions.
In~\cite{kswz-erptd-20}, a preliminary version of CH-Potentials\footnote{
In~\cite{kswz-erptd-20}, CH-Potentials are only used as a blackbox referring to an early ArXiv preprint~\cite{strasser2019perfect} of ours.
The paper does not describe any of the contribution of this paper.
} is used for such a scenario.
The work considers time-dependent blocked edges and waiting at parking locations.
Further, a trade-off between arrival time and route quality is considered.
\todo{cite correct Closures Version}

>>>>

There is a lot of work that extends hierarchical speed-up techniques to more complex settings.
\todo{cite overview}
% For example, in~\cite{fns-opca-14,gks-rpfof-10} multi-criteria optimization is studied.
MLD/CRP~\cite{dgpw-crprn-13} was developed to allow exchanging weights in reasonable time.
This enable user preferences and live traffic.
MLD/CRP also supports turn costs.
Integrating traffic predictions into CRP was studied in~\cite{bdpw-dtdrp-16}.
In~\cite{dsw-cch-15}, CH is extended to Customizable CH (CCH), which also supports exchanging weights and thus supporting user preferences and live traffic.
CH is extended to support turn costs in~\cite{}, CCH in~\cite{bwzz-cchtc-20}.
Traffic predictions are combined with CH in~\cite{swz-sfert-20,bgsv-mtdtt-13}.
\todo{cite correct CATCHUp Version}
\todo{improve! and discuss hierarchical extensions and what they achieve and their difficulties in more details}
Specialized variants for electric vehicle routing are developed in~\cite{DBLP:journals/algorithmica/BaumDPSWZ20,DBLP:conf/aaai/EisnerFS11}.
While these works show that it is possible to extend hierarchical approaches, they also show that it is non-trivial.
Further, in every setting the flexibility available at query time is fairly limited.
Combining all these hierarchical extensions is an unsolved problem.
%
CH-Potentials is not the first work to combine hierarchical approaches and A*~\cite{bdsssw-chgds-10,gkw-blwr-07,bdgwz-sfpcs-19}.
However, a lot of past works use A* to accelerate hierarchical approaches even further and loose A*'s flexibility.
\todo{cite traffic aware routing}
%

@@

The classical shortest path problem assumes that edge weights are scalars.
However in practice, travel times vary along an edge.
The primary reason is traffic.
Recurring traffic can be predicted by observing the traffic in the past.
It is common \cite{bgsv-mtdtt-13,bdpw-dtdrp-16,swz-sfert-20} to represent these predictions as \emph{travel time functions}.
An edge weight is no longer a scalar value but a function that maps the entry time onto the traversal time.
% Performing this prediction is outside of the scope of this paper.
It is common to refer to routing with predicted traffic as \emph{time-dependent routing}.
% Again, we first formalize the extended problem setting and then describe our solution with CH-Potentials.

@@

With this setup, we extended CH-Potentials to support time-dependent routing.
As we were able to keep all travel time functions out of the CH, we avoid a lot of algorithmic complications compared to~\cite{bgsv-mtdtt-13,bdpw-dtdrp-16,swz-sfert-20}, which create shortcuts of travel time functions to combine hierarchical speedup techniques with time-dependent routing.

@@

Truck routing differs from car routing due to night driving bans and other restrictions.
In~\cite{kswz-erptd-p-20}, a preliminary version of CH-Potentials\footnote{
In~\cite{kswz-erptd-p-20}, CH-Potentials are used as a blackbox referring to an early ArXiv preprint~\cite{strasser2019perfect} of ours.
The paper does not describe any of the contribution of this paper.
} is used for such a scenario.
The work considers time-dependent blocked edges and waiting at parking locations.
Further, a trade-off between arrival time and route quality is considered.
